---
title: "Random Forest Regresion"
output: html_notebook
---

```{r}
library(readr)
data <- read_csv("Position_Salaries.csv")
View(data)
```

```{r}
data = data[ , 2:3]
data
```


```{r}
# Fit the Random forest model to the dataset
library(randomForest)
```

### With 10 trees
```{r}
# data[1]- give you a dataframe , data$Salary would give you a vector. Which is how you should define the varables
set.seed(1234)
regressor = randomForest(x = data[1] , y = data$Salary, ntree = 10)
```


```{r}
# Predicting a new result with Random Forest Regression
y_pred = predict(regressor, data.frame(Level = 7.5))
y_pred
```
This is close to the amount the employee said he earned,$250k. Lets tree 100 trees and see if it is closer to his claim. 

```{r}
# Visualising the Random Forest Regression results (higher resolution)
library(ggplot2)
x_grid = seq(min(data$Level), max(data$Level), 0.01)
ggplot() +
  geom_point(aes(x = data$Level, y = data$Salary),
             colour = 'red') +
  geom_line(aes(x = x_grid, y = predict(regressor, newdata = data.frame(Level = x_grid))),
            colour = 'blue') +
  ggtitle('Truth or Bluff (Random Forest Regression)') +
  xlab('Level') +
  ylab('Salary')
```

### With 100 trees
```{r}
set.seed(1234)
regressor = randomForest(x = data[1] , y = data$Salary, ntree = 100)
```


```{r}
# Predicting a new result with Random Forest Regression
y_pred = predict(regressor, data.frame(Level = 7.5))
y_pred
```
This result is even futher from the supposed salary he claimed to earn. Lets try with 500 trees and see if its better.

```{r}
# Visualising the Random Forest Regression results (higher resolution)
library(ggplot2)
x_grid = seq(min(data$Level), max(data$Level), 0.01)
ggplot() +
  geom_point(aes(x = data$Level, y = data$Salary),
             colour = 'red') +
  geom_line(aes(x = x_grid, y = predict(regressor, newdata = data.frame(Level = x_grid))),
            colour = 'blue') +
  ggtitle('Truth or Bluff (Random Forest Regression)') +
  xlab('Level') +
  ylab('Salary')
```

### With 500 trees
```{r}
set.seed(1234)
regressor = randomForest(x = data[1] , y = data$Salary, ntree = 500)
```


```{r}
# Predicting a new result with Random Forest Regression
y_pred = predict(regressor, data.frame(Level = 7.5))
y_pred
```


```{r}
# Visualising the Random Forest Regression results (higher resolution)
library(ggplot2)
x_grid = seq(min(data$Level), max(data$Level), 0.01)
ggplot() +
  geom_point(aes(x = data$Level, y = data$Salary),
             colour = 'red') +
  geom_line(aes(x = x_grid, y = predict(regressor, newdata = data.frame(Level = x_grid))),
            colour = 'blue') +
  ggtitle('Truth or Bluff (Random Forest Regression)') +
  xlab('Level') +
  ylab('Salary')
```

So we see that the more trees we have the farther we are from the employees claim. From this results we can conclude he is most likely not being honest about how much he earned.